Bayesian Shape Reconstruction and Optimal Guidance for Autonomous Landing on Asteroids

### 2019-03-05 manuscript.tex
Move some more figures

\begin{figure}[htbp]
    \centering
    \input{tikz/geographos_metrics.tikz}
    \caption{Normalized uncertainty and volume percent error for Geographos\label{fig:geographos_metrics}}
\end{figure}

\paragraph{Asteroid \num{6489} Golevka Reconstruction} 
Next, \num{6489} Golevka is a small angular shaped asteroid of the Apollo group.
Discovered in \num{1995}, Golevka is a potentially hazardous asteroid which passes sufficiently close to the Earth to present a hazard.
\Cref{fig:golevka_reconstruction} shows the shape reconstruction for asteroid Golevka at several distinct points during the process.
\begin{figure}[htbp]
    \centering
    \subcaptionbox{Initial Shape Estimate\label{fig:golevka_partial_0}}{\includegraphics[trim={20cm 5cm 20cm 5cm},clip,keepaspectratio,width=0.5\textwidth,height=0.25\textheight]{figures/mesh_update/golevka/partial_0.jpg}}%
    \subcaptionbox{\SI{25}{\percent} of measurements added\label{fig:golevka_partial_25}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,width=0.5\textwidth,height=0.25\textheight]{figures/mesh_update/golevka/partial_1321.jpg}}\\%

    \subcaptionbox{\SI{50}{\percent} of measurements added\label{fig:golevka_partial_50}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,width=0.5\textwidth,height=0.25\textheight]{figures/mesh_update/golevka/partial_2643.jpg}}%
    \subcaptionbox{\SI{75}{\percent} of measurements added\label{fig:golevka_partial_75}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,width=0.5\textwidth,height=0.25\textheight]{figures/mesh_update/golevka/partial_3964.jpg}}\\%

    \subcaptionbox{\SI{100}{\percent} of measurements added\label{fig:golevka_partial_100}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,width=0.5\textwidth,height=0.25\textheight]{figures/mesh_update/golevka/partial_5285.jpg}}%
    \subcaptionbox{True Shape Model\label{fig:golevka_truth}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,width=0.5\textwidth,height=0.25\textheight]{figures/mesh_update/golevka/truth.jpg}}
    \caption[Asteroid Golevka incremental reconstruction]{Incremental reconstruction of asteroid Golevka~\label{fig:golevka_reconstruction}}
\end{figure}
Comparing~\cref{fig:golevka_partial_100,fig:golevka_truth} shows that the final shape closely matches the true radar model.
In~\cref{fig:golevka_metrics} we display the vertex uncertainty and mesh volume as a function of time.

\begin{figure}[htbp]
    \centering
    \input{tikz/golevka_metrics.tikz}
    \caption{Normalized uncertainty and volume percent error for Golevka\label{fig:golevka_metrics}}
\end{figure}

@@

\clearpage\newpage
\section{Optimal Guidance for Shape Reconstruction}\label{sec:explore_asteroid}

@@

\begin{figure}[htbp]
    \centering
    \subcaptionbox{Initial Shape Estimate\label{fig:52760_partial_weights_0}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/52760/partial_weights_1.jpg}}%
    \subcaptionbox{\SI{25}{\percent} of measurements\label{fig:52760_partial_weights_25}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/52760/partial_weights_3749.jpg}}%

    \subcaptionbox{\SI{50}{\percent} of measurements\label{fig:52760_partial_weights_50}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/52760/partial_weights_7499.jpg}}
    \subcaptionbox{\SI{75}{\percent} of measurements\label{fig:52760_partial_weights_75}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/52760/partial_weights_11249.jpg}}%

    \subcaptionbox{\SI{100}{\percent} of measurements\label{fig:52760_partial_weights_100}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/52760/partial_weights_14998.jpg}}%
    \subcaptionbox{True Shape Model\label{fig:52760_weights_truth}}{\includegraphics[trim={15cm 0cm 15cm 5cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{figures/mesh_update/52760/truth.jpg}}
    \caption[Asteroid 52760 shape reconstruction with uncertainty]{Incremental reconstruction of asteroid 52760. The images colored according to the shape uncertainty. Areas of high uncertainty are in yellow while ares of low uncertainty are in purple.~\label{fig:52760_weights_reconstruction}}
\end{figure}

>>>>

\begin{figure}[htbp]
    \centering
    \input{geographos_metrics.tikz}
    \caption{Normalized uncertainty and volume percent error for Geographos\label{fig:geographos_metrics}}
\end{figure}

\paragraph{Asteroid \num{6489} Golevka Reconstruction} 
Next, \num{6489} Golevka is a small angular shaped asteroid of the Apollo group.
Discovered in \num{1995}, Golevka is a potentially hazardous asteroid which passes sufficiently close to the Earth to present a hazard.
\Cref{fig:golevka_reconstruction} shows the shape reconstruction for asteroid Golevka at several distinct points during the process.
\begin{figure}[htbp]
    \centering
    \subcaptionbox{Initial Shape Estimate\label{fig:golevka_partial_0}}{\includegraphics[trim={20cm 5cm 20cm 5cm},clip,keepaspectratio,width=0.5\textwidth,height=0.25\textheight]{mesh_update_golevka_partial_0.jpg}}%
    \subcaptionbox{\SI{25}{\percent} of measurements added\label{fig:golevka_partial_25}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,width=0.5\textwidth,height=0.25\textheight]{mesh_update_golevka_partial_1321.jpg}}\\%

    \subcaptionbox{\SI{50}{\percent} of measurements added\label{fig:golevka_partial_50}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,width=0.5\textwidth,height=0.25\textheight]{mesh_update_golevka_partial_2643.jpg}}%
    \subcaptionbox{\SI{75}{\percent} of measurements added\label{fig:golevka_partial_75}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,width=0.5\textwidth,height=0.25\textheight]{mesh_update_golevka_partial_3964.jpg}}\\%

    \subcaptionbox{\SI{100}{\percent} of measurements added\label{fig:golevka_partial_100}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,width=0.5\textwidth,height=0.25\textheight]{mesh_update_golevka_partial_5285.jpg}}%
    \subcaptionbox{True Shape Model\label{fig:golevka_truth}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,width=0.5\textwidth,height=0.25\textheight]{mesh_update_golevka_truth.jpg}}
    \caption[Asteroid Golevka incremental reconstruction]{Incremental reconstruction of asteroid Golevka~\label{fig:golevka_reconstruction}}
\end{figure}
Comparing~\cref{fig:golevka_partial_100,fig:golevka_truth} shows that the final shape closely matches the true radar model.
In~\cref{fig:golevka_metrics} we display the vertex uncertainty and mesh volume as a function of time.

\begin{figure}[htbp]
    \centering
    \input{golevka_metrics.tikz}
    \caption{Normalized uncertainty and volume percent error for Golevka\label{fig:golevka_metrics}}
\end{figure}

@@

\section{Optimal Guidance for Shape Reconstruction}\label{sec:explore_asteroid}

@@

\begin{figure}[htbp]
    \centering
    \subcaptionbox{Initial Shape Estimate\label{fig:52760_partial_weights_0}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{dynamic_exploration_52760_partial_weights_1.jpg}}%
    \subcaptionbox{\SI{25}{\percent} of measurements\label{fig:52760_partial_weights_25}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{dynamic_exploration_52760_partial_weights_3749.jpg}}%

    \subcaptionbox{\SI{50}{\percent} of measurements\label{fig:52760_partial_weights_50}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{dynamic_exploration_52760_partial_weights_7499.jpg}}
    \subcaptionbox{\SI{75}{\percent} of measurements\label{fig:52760_partial_weights_75}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{dynamic_exploration_52760_partial_weights_11249.jpg}}%

    \subcaptionbox{\SI{100}{\percent} of measurements\label{fig:52760_partial_weights_100}}{\includegraphics[trim={30cm 15cm 30cm 15cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{dynamic_exploration_52760_partial_weights_14998.jpg}}%
    \subcaptionbox{True Shape Model\label{fig:52760_weights_truth}}{\includegraphics[trim={15cm 0cm 15cm 5cm},clip,height=0.25\textheight,width=0.5\textwidth,keepaspectratio]{mesh_update_52760_truth.jpg}}
    \caption[Asteroid 52760 shape reconstruction with uncertainty]{Incremental reconstruction of asteroid 52760. The images colored according to the shape uncertainty. Areas of high uncertainty are in yellow while ares of low uncertainty are in purple.~\label{fig:52760_weights_reconstruction}}
\end{figure}
